\ttitle

### 2015-06-05 Chapters/Introduction.tex
CPET in Thoracic Surgery - complete
- 2 reviews included
- First - a meta-analysis by Benzo et al
- Second, ACCP recommendations by Colice et al

\subsection{Thoracic Surgery}

>>>>

\subsection{Thoracic Surgery}
The role of cardiopulmonary exercise testing in patient undergoing non-cardiac thoracic surgery has been well established for over a decade. In a recent meta-analysis of 14 studies, Benzo and co-workers reported on 955 patients who underwent cardiopulmonary exercise tests as part of their preoperative work-up before lung resection for cancer. $\dot{V}_{O_2}$Max (ml/kg/min), $\dot{V}_{O_2}$Max (\% predicted), maximum exercise load achieved (Watts) and FEV1 (\% predicted) were all significantly higher in patients who recovered with no postoperative complications. They also found that the mean $\dot{V}_{O_2}$Max in patients who did not develop complications was approximately 20 ml/kg/min and the mean $\dot{V}_{O_2}$Max in patients who developed complications was 15 ml/kg/min across all studies. This would suggest that cardiopulmonary exercise testing can offer clinically useful thresholds across different populations that can be used to risk stratify patients.\parencite{benzo_complications_2007}

The 2$^nd$ edition of the American College of Chest Physicians' Evidence-Based Clinical Practice Guidelines for the 'Physiologic evaluation of the patient with lung cancer being considered for resectional surgery' recommends that patients with a low $\dot{V}_{O_2}$Max ($<10$ ml/kg/min) or with low $\dot{V}_{O_2}$Max ($<15$ ml/kg/min) associated with other risk factors on spirometry and cardiopulmonary exercise testing should be counselled about non-operative treatment options and non-standard surgery as the risk of perioperative death and cardiopulmonary complications was very high. The 1C grading of this recommendation not only represents the observational nature of most of the studies it is based on but also that such observational evidence is sufficiently consistent\parencite{benzo_complications_2007} to make a strong recommendation.\parencite{colice_physiologic_2007}
